---
title: "Filter"
author: "Nick Wawee"
date: "3/22/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
```

## Filter


```{r loading}
df = read.csv('../data/raw/BankChurners.csv', stringsAsFactors = T)
```

The original data set contains `r ncol(df)` variables and `r nrow(df)` customers. The code below will filter the customer churn dataset for all unknown or missing values.

### Remove Naive Bayes Columns

The Naive Bayes columns will be removed because they are not a part of the analysis.

```{r naive bayes}
df = df[,c(-22,-23)]
```

### Categorical Variables

Next the categorical variables will be filtered to not have any unknowns.

```{r cat vars}
cvars = c('Attrition_Flag', 'Gender', 'Education_Level', 'Marital_Status', 'Income_Category',
          'Card_Category')

for (c in cvars){
  numunk = length(which(df[, c] == 'Unknown'))
  cat('The', c, 'variable has',numunk, 'unknowns.\n')
}

```

The education level, marital status, and income category variables with unkown observations will be filtered out.

```{r filter out cats}
df = df[-which(df[, 'Education_Level'] == 'Unknown'), ]
df = df[-which(df[, 'Marital_Status'] == 'Unknown'), ]
df = df[-which(df[, 'Income_Category'] == 'Unknown'), ]
```

### Numerical Variables

```{r check num vars}
`%notin%` <- Negate(`%in%`)
numvars = colnames(df)[colnames(df) %notin% cvars]

for (v in numvars){
  numunk = length(which(is.na(df[, v])))
  cat('The', v, 'variable has',numunk, 'NAs.\n')
}
```


```{r save}
write.csv(x = df, file = '../data/processed/BankChurners_filtered.csv')
```